%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
  {Senior Software Engineer} % Job title
  {EVBox} % Organization
  {Amsterdam, Netherlands} % Location
  {Jun. 2023 - Present} % Date(s)
  {
    Contributing to Everon at EVBox, optimizing backend systems for efficient and reliable operation of charging stations and advancing sustainable transportation solutions. Handling over 12 million charging sessions yearly, our team is dedicated to empowering the global EV community.
  }
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Enabled Prometheus and Grafana monitoring for the transaction service, improving visibility and streamlining maintenance processes.}
      \item {Refactored and optimized the monthly subscription cost calculation, reducing processing time by 90\%, and implemented individual transactions for each subscription to enable isolated retries.}
      \item {Efficiently migrated legacy application from Google Guice to Spring Boot, enhancing performance and maintainability.}
      \item {Utilized GCP's cloud infrastructure for project operations.}
      \item {Mentoring junior developers.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Mobiquity} % Organization
    {Amsterdam, Netherlands} % Location
    {Sep. 2021 - May 2023} % Date(s)
    {
      At Mobiquity, a digital consultancy focusing on digital product delivery, I collaborated with SurePay, a market leader with over 22\% of the UK IBAN name check market share and 100\% in the Netherlands.
    }
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed REST APIs consumed by multiple banks and organizations in the UK.}
        \item {Responsible for automating the onboarding of new banks via the Pay.UK open banking specification.}
        \item {Improved and refactored secondary identification service, which increased performance by 70\%.}
        \item {Managed project resources on AWS cloud infrastructure.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Java Developer} % Job title
    {Snapp!} % Organization
    {Tehran, Iran} % Location
    {Sep. 2020 - Aug. 2021} % Date(s)
    {
      Snapp! is the first and leading ride-hailing application in Iran. Snapp handles more than 4 million rides per day and serves over 60 million customers annually. I was part of the Snapp Fintech team, where we focused on developing a payment hub for Snapp products, facilitating users' daily payments.
    }
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented different payment solutions, such as Buy Now, Pay Later (BNPL), and wallet.}
        \item {Developed API Gateway, which proxies the services and authorizes the requests.}
        \item {Contributed as a member of the Fintech team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Java Developer} % Job title
    {MyDigipay} % Organization
    {Tehran, Iran} % Location
    {Mar. 2019 - Aug. 2020} % Date(s)
    {
      Mydigipay is part of the Digikala Group, Iran's first and largest reference for reviewing and selling goods online. We worked on building payment products that offer the easiest and secure e-payment experience for individuals and businesses.
    }
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed the Installment module.}
        \item {Designed and implemented the KYC (Know Your Customer) module.}
        \item {Recognized as one of the best developers of 2019 by colleagues' survey results.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Java Developer} % Job title
    {Sava Arman Kish} % Organization
    {Tehran, Iran} % Location
    {Jul. 2018 - Mar. 2019} % Date(s)
    {
      We designed and developed a cryptocurrency exchange.
    }
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented the Order module.}
        \item {Designed and implemented the Notification module.}
        \item {Designed and implemented the Report module.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Developer} % Job title
    {Navaco (Maskan Bank)} % Organization
    {Tehran, Iran} % Location
    {Feb. 2017 - Jul. 2018} % Date(s)
    {
      Maskan Bank is one of the biggest banks in Iran with more than 1100 branches. We developed a web-based program for implementing banking operations for Maskan Bank.
    }
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed as part of the Lending team.}
        \item {Designed and implemented lending overnight calculation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Developer} % Job title
    {Hamgam Corporate Group} % Organization
    {Tehran, Iran} % Location
    {Apr. 2014 - Jan. 2017} % Date(s)
    {
      Hamgam provides leading-edge IT and consultancy services and solutions to large organizations and companies.
    }
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented the Sale module.}
        \item {Designed and implemented the Inventory module.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
